%!TEX root = design_doc.tex


\section{Schedule}

\subsection{Design Document and Presentation}

We will produce the design document which is a fairly detailed description of
the project, and it will be submitted by 11/30/2016.

We will produce the design presentation slides, and make an oral presentation in
class on 12/01/2016, which will give an overview of the project, and discuss
specifics of the design.


\subsection{Prototype}

In this release, we will have at least one implementation for each step.

Zongxi and Wenyan will develop the implementation of AR and MA in the ``Model''
class, and take some sample data for testing. Qingcan will develop the
implementation of gradient descent method in the ``Optimization'' class.
Zhuoran will develop the implementation of correlation testing in ``Inference''
class. Cong will develop the interface for ``Model'', ``Optimization'' and
``Inference'' class. Hao will develop one method in ``Clustering'' class.


\subsection{Alpha Version}

In this release, we will complete most methods in each class.

Zongxi will continue working on combination methods in the ``Model'' class.
Wenyan will develop the ``Simulation'' class. Qingcan will finish the
``Optimization'' class. Zhuoran will implement confidence interval and
hypothesis testing in the ``Inference'' class. Hao will finish the
``Clustering'' class. Cong will provide interface for ``Simulation'' and
``Clustering'' class.


\subsection{Final Version}

In this relase, we will impelement the ``Visualization'' class, and compelet all
the code, then get more data for testing. We will also finish the software
manual and project report.
