%!TEX root = design_doc.tex


\section{Overview}

Time series analysis comprises methods for analyzing time series data in order to extract meaningful statistics and other characteristics of the data. It's widely used in statistics, signal processing, pattern recognition, mathematical finance, weather forecasting, earthquake prediction, control engineering, and largely in any domain of applied science and engineering which involves temporal measurements. In this project, we will play a game with time series in finance. It has gained its popularity in Wall Street recently, since it is fundamental to the most promising quantitative investment strategies. 

We develop a system that can predict future prices of stocks, with different time series models. Given input of a stock price series, our system will first fit some powerful and popular time series models, such as autoregressive (AR) model, moving average (MA) model and other derived models. This procedure will give you the estimation of parameters in these models. The most important task in estimation is the optimization procedure. Users can select one of optimization methods in the system based on their preference. The optimization method includes but not limited to gradient descent and Newton's method.

After model fitting and estimation, our system provides a fast way to do statistical inference. Users can do different kinds of statistical test as well as confidence interval. Moreover, with fitted model, future price prediction is made and it's compared with real price data. Moreover, we provide different methods to assess the prediction accuracy, which will be visualized afterwards.

More interestingly, if users input multiple stock prices, we can divide these stocks into different groups, which is called clustering. Among each group, stocks share similarity. Different clusters will also be visualized.

In the following, we will present the basic organization and components.

